The SMT Competition 2015--2018

### 2019-03-14 2018/report/SMT-COMP.tex
Consistent track names.

%% Changes 2016:
%% \begin{itemize}
%% \item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
%%   language.  \emph{Rationale:} This is the latest version of the
%%   SMT-LIB language.  It was released on 2015-06-28, and is largely
%%   backwards-compatible to version~2.0, which was used for SMT-COMP
%%   2015.
%% \item Solver output may affect the score even when the solver does not
%%   terminate within the time limit.  (In 2015, main track solver output
%%   was ignored if the solver subsequently timed out.)  Solvers should
%%   take care not to accidentally produce output that contains
%%   \texttt{sat} or \texttt{unsat} even when they are killed.
%%   \emph{Rationale:} Users are likely to trust solver responses even
%%   when the solver continues to run for some time.
%% \item Divisions for floating-point arithmetic are no longer
%%   experimental, and will be considered competitive if the necessary
%%   requirements (see Section~\ref{sec:scoring}) are met.
%%   \emph{Rationale:} Floating-point divisions were experimental in
%%   2015.  By now, their definition is sufficiently stable, and they are
%%   supported by several solvers.
%% \item Division scores will be based on a weighted sum of scores for
%%   benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
%%   have had sufficient computational resources to evaluate all solver
%%   entrants on all eligible benchmarks.  As a side-effect, the
%%   weighting of benchmark families that was achieved in early SMT-COMPs
%%   through a careful selection of benchmarks (based on benchmark
%%   difficulty and category) was lost.  Since there are vast differences
%%   in size between benchmark families, we believe that a weighting that
%%   de-emphasizes large benchmark families (see
%%   Section~\ref{sec:division-scoring}) will lead to more meaningful
%%   competition results.
%% \item The unsat-core track that was introduced in SMT-COMP 2012, but
%%   discontinued in 2013-2015 (partly because of the competition's move
%%   to StarExec), is back.  It will be experimental in 2016; its results
%%   will be reported, but no official winners will be announced.
%%   \emph{Rationale:} Unsat cores are important in many applications of
%%   SMT solving.  The track was discontinued primarily for
%%   infrastructure and resource reasons.  We are pleased that we can
%%   finally offer it again, but we ask for your understanding in case of
%%   mishaps while we port the required tools.
%% \item Best industrial performance will no longer be recognized
%%   separately.  \emph{Rationale:} While there is agreement in the SMT
%%   community to emphasize problems that come from real applications,
%%   industrial performance largely coincided with overall performance in
%%   SMT-COMP 2015.  We consider the effort to determine and report it
%%   separately no longer justified.
%% \end{itemize}

%% Changes 2017:
%% \begin{itemize}
%% \item Submission of accompanying information for solvers is via a web
%%   form (rather than by email to the organizers).  \emph{Rationale:}
%%   Email submissions were often incomplete, leading to ambiguity and
%%   further inquiries.  The form provides a more structured way of
%%   submitting information.
%% \item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
%%   language.  \emph{Rationale:} This is the latest version of the
%%   SMT-LIB language.  It is largely backwards-compatible with earlier
%%   versions (in particular~2.0 and~2.5).
%% \item Benchmarks that use partial bit-vector functions, such as
%%   \texttt{bvudiv}, or underspecified floating-point functions, such as
%%   \texttt{fp.min}, will be eligible for the competition again.
%%   \emph{Rationale:} A conclusion on the semantics of these functions
%%   has finally been reached, and the status of affected SMT-LIB
%%   benchmarks has been updated accordingly.
%% \item Benchmarks with unknown status will be eligible for the
%%   competition's main track.  In 2016, solver performance on benchmarks
%%   with unknown status was evaluated but reported separately; in 2017,
%%   it will directly affect the competition results.  \emph{Rationale:}
%%   Using only benchmarks with known status (i.e., benchmarks that have
%%   been solved before) to determine the competition results unjustly
%%   favors imitation of existing solvers over true innovation.
%% \item In the competition-wide scoring, the (per-division) penalty for
%%   erroneous results is changed from the number of errors to a fixed
%%   constant (multiplied by the weight of the respective division).
%%   \emph{Rationale:} The weight already takes the number of benchmarks
%%   in the division into account; multiplying it by the number of errors
%%   overemphasizes large divisions.
%% \item The unsat-core track, which was re-introduced in 2016, is no
%%   longer experimental.  Its divisions will be considered competitive
%%   if the necessary requirements (see Section~\ref{sec:scoring}) are
%%   met.  \emph{Rationale:} Rules and tool support for the unsat-core
%%   track proved sufficiently stable in 2016.
%% \item The competition will feature experimental divisions for
%%   benchmarks that use algebraic datatypes.  \emph{Rationale:}
%%   Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
%%   which is expected to become official in the near future, and are
%%   already supported by some solvers.  Benchmarks that use datatypes
%%   have recently been added to SMT-LIB.
%% \end{itemize}

%% Changes 2018:
%% \begin{itemize}
%% \item The time limit per solver/benchmark pair is anticipated to be at
%%   most 20 minutes in the main track, and at most 40 minutes in the
%%   other tracks.  \emph{Rationale:} Already in 2017, the time limit for
%%   the main track was reduced to 20 minutes (down from 40 minutes in
%%   earlier years) to cope with the inclusion of a large number of
%%   benchmarks with unknown status.
%% \item In the unsat-core track, the unsatisfiability check for the
%%   returned core will be based on a simple majority vote.  The case
%%   that a solver finds its own core satisfiable will no longer be
%%   treated specially.  \emph{Rationale:} This allows to simplify the
%%   post-processing of unsat-core track results considerably.
%% \item In 2017, the competition featured experimental divisions for
%%   benchmarks that use algebraic datatypes.  These divisions will be
%%   regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
%%   datatypes are specified in the latest official release (Version~2.6)
%%   of the SMT-LIB standard.
%% \item The competition will feature an experimental divisions for
%%   benchmarks that use strings.  \emph{Rationale:} Corresponding
%%   theories and benchmarks are expected to be added to SMT-LIB in the
%%   near future.
%% \end{itemize}

@@

The SMT Competition consists of several tracks.  The \emph{main
  track}, which has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{application track}, which has been part of the competition since
2011~\cite{BDdMOS13}, features incremental benchmarks.  These
benchmarks are passed to each solver one command at a time by a trace
executor, which waits for the solver's response before passing the
next benchmark command (to prevent look-ahead behavior).  The
\emph{unsat-core track} uses main-track benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but still unsatisfiable
subset of the benchmark's assertions).  The unsat-core track had first
been part of the competition in 2012~\cite{CGBD12}, but was then
discontinued partly because of the competition's move to StarExec and
lacking tool support.  It was re-introduced as an experimental track
in 2016, and has been a regular competition track again since~2017.

@@

\begin{table}
  \caption{Number of divisions in each competition track}
  \label{table:divisions}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    Main track        &  40 & 40 & 49 & 50 \\
    Application track &  14 & 14 & 16 & 21 \\
    Unsat-core track  &  -- & 40 & 41 & 44 \\
    \bottomrule
  \end{tabular}
\end{table}

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers.''~\cite{CSW15} Together with the increased
computational resources available to the competition since its move to
StarExec, this finding prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible benchmarks.
This change had an unintended side effect: the pseudo-random selection
process had been purposely constrained to choose benchmarks from
different benchmark families (that is, groups of benchmarks with
similar characteristics).  Since there are vast differences in size
between benchmark families in the SMT Library, the competition
since~2016 uses a scoring method that assigns a weight to each
main-track benchmark in order to de-emphasize large benchmark
families~\cite{rules18}.

Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
favoring imitation of existing solvers over true innovation.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's main track regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound) solvers.  Benchmarks with
disagreements are removed from the competition results.  In 2016,
there were disagreements on 79 benchmarks; in 2017, only one benchmark
was removed; and in 2018, there were no disagreements between
otherwise sound solvers.

For incremental benchmarks, the situation is different: an incremental
benchmark is ineligible for the application track if its first {\tt
  check-sat} command has unknown status.  Otherwise, the prefix of the
benchmark that only contains {\tt check-sat} commands with known
status is eligible.  The main reason for this difference is that the
competition tools for the application track (in particular, the trace
executor) have not been adapted yet to support {\tt check-sat}
commands with unknown status.

@@

\begin{table}
  \caption{Number of benchmarks used in the main track (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \midrule
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \bottomrule
  \end{tabular}}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the application track (by
    division)}
  \label{table:benchmarks-application-track}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ALIA       &   24 &   24 &   24 &   24 \\
    ANIA       &    3 &    3 &    3 &    3 \\
    AUFNIRA    &   -- &   -- &   -- &  117 \\
    BV         &   -- &   -- &   -- &   17 \\
    LIA        &    6 &    6 &    6 &    6 \\
    QF\_ABV    &   -- &   -- &   -- &   15 \\
    QF\_ALIA   &   44 &   44 &   44 &   44 \\
    QF\_ANIA   &    5 &    5 &    5 &    5 \\
    QF\_AUFBV  &   -- &   -- &   -- &   10 \\
    QF\_AUFLIA &   72 &   72 &   72 &   72 \\
    QF\_BV     &   18 &   18 &   18 &  815 \\
    QF\_BVFP   &   -- &   -- &    2 &    2 \\
    QF\_FP     &   -- &   -- &    2 &    2 \\
    QF\_LIA    &   65 &   69 &   68 &   69 \\
    QF\_LRA    &   10 &   10 &   10 &   10 \\
    QF\_NIA    &   10 &   10 &   10 &   10 \\
    QF\_UFBV   &   -- &   -- &   -- & 2327 \\
    QF\_UFLIA  &  905 &  905 &  780 &  780 \\
    QF\_UFLRA  & 3331 & 3331 & 3056 & 3058 \\
    QF\_UFNIA  &    1 &    1 &    1 &    1 \\
    UFLRA      & 5358 & 5358 & 1870 & 1870 \\
    \midrule
    Total      & 9852 & 9856 & 5971 & 9257 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

%% Changes 2016:
%% \begin{itemize}
%% \item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
%%   language.  \emph{Rationale:} This is the latest version of the
%%   SMT-LIB language.  It was released on 2015-06-28, and is largely
%%   backwards-compatible to version~2.0, which was used for SMT-COMP
%%   2015.
%% \item Solver output may affect the score even when the solver does not
%%   terminate within the time limit.  (In 2015, main track solver output
%%   was ignored if the solver subsequently timed out.)  Solvers should
%%   take care not to accidentally produce output that contains
%%   \texttt{sat} or \texttt{unsat} even when they are killed.
%%   \emph{Rationale:} Users are likely to trust solver responses even
%%   when the solver continues to run for some time.
%% \item Divisions for floating-point arithmetic are no longer
%%   experimental, and will be considered competitive if the necessary
%%   requirements (see Section~\ref{sec:scoring}) are met.
%%   \emph{Rationale:} Floating-point divisions were experimental in
%%   2015.  By now, their definition is sufficiently stable, and they are
%%   supported by several solvers.
%% \item Division scores will be based on a weighted sum of scores for
%%   benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
%%   have had sufficient computational resources to evaluate all solver
%%   entrants on all eligible benchmarks.  As a side-effect, the
%%   weighting of benchmark families that was achieved in early SMT-COMPs
%%   through a careful selection of benchmarks (based on benchmark
%%   difficulty and category) was lost.  Since there are vast differences
%%   in size between benchmark families, we believe that a weighting that
%%   de-emphasizes large benchmark families (see
%%   Section~\ref{sec:division-scoring}) will lead to more meaningful
%%   competition results.
%% \item The Unsat-Core track that was introduced in SMT-COMP 2012, but
%%   discontinued in 2013-2015 (partly because of the competition's move
%%   to StarExec), is back.  It will be experimental in 2016; its results
%%   will be reported, but no official winners will be announced.
%%   \emph{Rationale:} Unsat cores are important in many applications of
%%   SMT solving.  The track was discontinued primarily for
%%   infrastructure and resource reasons.  We are pleased that we can
%%   finally offer it again, but we ask for your understanding in case of
%%   mishaps while we port the required tools.
%% \item Best industrial performance will no longer be recognized
%%   separately.  \emph{Rationale:} While there is agreement in the SMT
%%   community to emphasize problems that come from real applications,
%%   industrial performance largely coincided with overall performance in
%%   SMT-COMP 2015.  We consider the effort to determine and report it
%%   separately no longer justified.
%% \end{itemize}

%% Changes 2017:
%% \begin{itemize}
%% \item Submission of accompanying information for solvers is via a web
%%   form (rather than by email to the organizers).  \emph{Rationale:}
%%   Email submissions were often incomplete, leading to ambiguity and
%%   further inquiries.  The form provides a more structured way of
%%   submitting information.
%% \item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
%%   language.  \emph{Rationale:} This is the latest version of the
%%   SMT-LIB language.  It is largely backwards-compatible with earlier
%%   versions (in particular~2.0 and~2.5).
%% \item Benchmarks that use partial bit-vector functions, such as
%%   \texttt{bvudiv}, or underspecified floating-point functions, such as
%%   \texttt{fp.min}, will be eligible for the competition again.
%%   \emph{Rationale:} A conclusion on the semantics of these functions
%%   has finally been reached, and the status of affected SMT-LIB
%%   benchmarks has been updated accordingly.
%% \item Benchmarks with unknown status will be eligible for the
%%   competition's main track.  In 2016, solver performance on benchmarks
%%   with unknown status was evaluated but reported separately; in 2017,
%%   it will directly affect the competition results.  \emph{Rationale:}
%%   Using only benchmarks with known status (i.e., benchmarks that have
%%   been solved before) to determine the competition results unjustly
%%   favors imitation of existing solvers over true innovation.
%% \item In the competition-wide scoring, the (per-division) penalty for
%%   erroneous results is changed from the number of errors to a fixed
%%   constant (multiplied by the weight of the respective division).
%%   \emph{Rationale:} The weight already takes the number of benchmarks
%%   in the division into account; multiplying it by the number of errors
%%   overemphasizes large divisions.
%% \item The Unsat-Core track, which was re-introduced in 2016, is no
%%   longer experimental.  Its divisions will be considered competitive
%%   if the necessary requirements (see Section~\ref{sec:scoring}) are
%%   met.  \emph{Rationale:} Rules and tool support for the unsat-core
%%   track proved sufficiently stable in 2016.
%% \item The competition will feature experimental divisions for
%%   benchmarks that use algebraic datatypes.  \emph{Rationale:}
%%   Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
%%   which is expected to become official in the near future, and are
%%   already supported by some solvers.  Benchmarks that use datatypes
%%   have recently been added to SMT-LIB.
%% \end{itemize}

%% Changes 2018:
%% \begin{itemize}
%% \item The time limit per solver/benchmark pair is anticipated to be at
%%   most 20 minutes in the main track, and at most 40 minutes in the
%%   other tracks.  \emph{Rationale:} Already in 2017, the time limit for
%%   the main track was reduced to 20 minutes (down from 40 minutes in
%%   earlier years) to cope with the inclusion of a large number of
%%   benchmarks with unknown status.
%% \item In the Unsat-Core track, the unsatisfiability check for the
%%   returned core will be based on a simple majority vote.  The case
%%   that a solver finds its own core satisfiable will no longer be
%%   treated specially.  \emph{Rationale:} This allows to simplify the
%%   post-processing of Unsat-Core track results considerably.
%% \item In 2017, the competition featured experimental divisions for
%%   benchmarks that use algebraic datatypes.  These divisions will be
%%   regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
%%   datatypes are specified in the latest official release (Version~2.6)
%%   of the SMT-LIB standard.
%% \item The competition will feature an experimental divisions for
%%   benchmarks that use strings.  \emph{Rationale:} Corresponding
%%   theories and benchmarks are expected to be added to SMT-LIB in the
%%   near future.
%% \end{itemize}

@@

The SMT Competition consists of several tracks.  The \emph{main
  track}, which has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{Application track}, which has been part of the competition since
2011~\cite{BDdMOS13}, features incremental benchmarks.  These
benchmarks are passed to each solver one command at a time by a trace
executor, which waits for the solver's response before passing the
next benchmark command (to prevent look-ahead behavior).  The
\emph{Unsat-Core track} uses Main-track benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but still unsatisfiable
subset of the benchmark's assertions).  The Unsat-Core track had first
been part of the competition in 2012~\cite{CGBD12}, but was then
discontinued partly because of the competition's move to StarExec and
lacking tool support.  It was re-introduced as an experimental track
in 2016, and has been a regular competition track again since~2017.

@@

\begin{table}
  \caption{Number of divisions in each competition track}
  \label{table:divisions}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    Main track        &  40 & 40 & 49 & 50 \\
    Application track &  14 & 14 & 16 & 21 \\
    Unsat-Core track  &  -- & 40 & 41 & 44 \\
    \bottomrule
  \end{tabular}
\end{table}

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers.''~\cite{CSW15} Together with the increased
computational resources available to the competition since its move to
StarExec, this finding prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible benchmarks.
This change had an unintended side effect: the pseudo-random selection
process had been purposely constrained to choose benchmarks from
different benchmark families (that is, groups of benchmarks with
similar characteristics).  Since there are vast differences in size
between benchmark families in the SMT Library, the competition
since~2016 uses a scoring method that assigns a weight to each
Main-track benchmark in order to de-emphasize large benchmark
families~\cite{rules18}.

Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
favoring imitation of existing solvers over true innovation.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's Main track regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound) solvers.  Benchmarks with
disagreements are removed from the competition results.  In 2016,
there were disagreements on 79 benchmarks; in 2017, only one benchmark
was removed; and in 2018, there were no disagreements between
otherwise sound solvers.

For incremental benchmarks, the situation is different: an incremental
benchmark is ineligible for the Application track if its first {\tt
  check-sat} command has unknown status.  Otherwise, the prefix of the
benchmark that only contains {\tt check-sat} commands with known
status is eligible.  The main reason for this difference is that the
competition tools for the Application track (in particular, the trace
executor) have not been adapted yet to support {\tt check-sat}
commands with unknown status.

@@

\begin{table}
  \caption{Number of benchmarks used in the Main track (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \midrule
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \bottomrule
  \end{tabular}}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the Application track (by
    division)}
  \label{table:benchmarks-application-track}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ALIA       &   24 &   24 &   24 &   24 \\
    ANIA       &    3 &    3 &    3 &    3 \\
    AUFNIRA    &   -- &   -- &   -- &  117 \\
    BV         &   -- &   -- &   -- &   17 \\
    LIA        &    6 &    6 &    6 &    6 \\
    QF\_ABV    &   -- &   -- &   -- &   15 \\
    QF\_ALIA   &   44 &   44 &   44 &   44 \\
    QF\_ANIA   &    5 &    5 &    5 &    5 \\
    QF\_AUFBV  &   -- &   -- &   -- &   10 \\
    QF\_AUFLIA &   72 &   72 &   72 &   72 \\
    QF\_BV     &   18 &   18 &   18 &  815 \\
    QF\_BVFP   &   -- &   -- &    2 &    2 \\
    QF\_FP     &   -- &   -- &    2 &    2 \\
    QF\_LIA    &   65 &   69 &   68 &   69 \\
    QF\_LRA    &   10 &   10 &   10 &   10 \\
    QF\_NIA    &   10 &   10 &   10 &   10 \\
    QF\_UFBV   &   -- &   -- &   -- & 2327 \\
    QF\_UFLIA  &  905 &  905 &  780 &  780 \\
    QF\_UFLRA  & 3331 & 3331 & 3056 & 3058 \\
    QF\_UFNIA  &    1 &    1 &    1 &    1 \\
    UFLRA      & 5358 & 5358 & 1870 & 1870 \\
    \midrule
    Total      & 9852 & 9856 & 5971 & 9257 \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the Unsat-Core track (by
    division)}
  \label{table:benchmarks-unsat-core-track}
  \centering
  \scalebox{1}[.91]{\begin{tabular}{lrrr}
    \toprule
    Division & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ALIA       &     41 &     41 &     41 \\
    AUFBVDTLIA &     -- &     -- &     25 \\
    AUFLIA     &      3 &      3 &      3 \\
    AUFLIRA    &  19749 &  19771 &  19771 \\
    AUFNIRA    &   1046 &   1050 &   1053 \\
    BV         &     56 &     94 &   4937 \\
    LIA        &    191 &    233 &    233 \\
    LRA        &    319 &   1106 &   1539 \\
    NIA        &      3 &      4 &      4 \\
    NRA        &   3788 &   3801 &   3801 \\
    QF\_ABV    &   4644 &   4673 &   4677 \\
    QF\_ABVFP  &     -- &   3934 &   3934 \\
    QF\_ALIA   &     80 &     80 &     80 \\
    QF\_ANIA   &      8 &      8 &      8 \\
    QF\_AUFBV  &     31 &     25 &     25 \\
    QF\_AUFLIA &    516 &    516 &    516 \\
    QF\_AUFNIA &     15 &     12 &     12 \\
    QF\_AX     &    279 &    279 &    279 \\
    QF\_BV     &  17172 &  23732 &  25700 \\
    QF\_BVFP   &      6 &   3174 &   3174 \\
    QF\_DT     &     -- &     -- &   4422 \\
    QF\_FP     &  17213 &  20028 &  20026 \\
    QF\_IDL    &    816 &    816 &    816 \\
    QF\_LIA    &   2840 &   2844 &   3019 \\
    QF\_LIRA   &      5 &      5 &      5 \\
    QF\_LRA    &    633 &    671 &    683 \\
    QF\_NIA    &    316 &   3130 &   4842 \\
    QF\_NIRA   &      2 &      2 &      2 \\
    QF\_NRA    &   4948 &   5296 &   5357 \\
    QF\_RDL    &    113 &    113 &    113 \\
    QF\_UF     &   4100 &   4101 &   4330 \\
    QF\_UFBV   &     31 &     31 &    575 \\
    QF\_UFIDL  &    335 &    322 &    322 \\
    QF\_UFLIA  &    195 &    183 &    183 \\
    QF\_UFLRA  &    853 &    511 &    511 \\
    QF\_UFNIA  &      7 &      7 &      7 \\
    QF\_UFNRA  &     18 &     11 &     11 \\
    UF         &   2039 &   3316 &   3442 \\
    UFBV       &     53 &     97 &     97 \\
    UFDT       &     -- &     -- &   1863 \\
    UFIDL      &     62 &     57 &     57 \\
    UFLIA      &   8377 &   7714 &   7743 \\
    UFLRA      &     20 &     10 &     10 \\
    UFNIA      &   2318 &   2432 &   2457 \\
    \midrule
    Total      &  93241 & 114233 & 130705 \\
    \bottomrule
  \end{tabular}}
\end{table}
